---
title: "Homework 6 Solutions"
author: Laura Gomez
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
library(tidyverse)
library(p8105.datasets)
library(dplyr)
require(gridExtra)
library(tidyverse)
library(modelr)
library(mgcv)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = 0.6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1

```{r}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```


Start with one city.

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")
glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```


Try this across cities.

```{r}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI")) 
```

```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```



# Problem 2

Import and tidy the following data set:
```{r Birth_weight_df}
Birth_weight_df = read_csv("./Data/birthweight (1).csv") %>%
  mutate(babysex = as.character(babysex), babysex = case_when(babysex == 1 ~ "male", babysex == 2 ~ "female" )) %>%
  mutate(frace = as.character(frace),
    frace = case_when(
      frace == 1 ~ "White", 
      frace == 2 ~ "Black", 
      frace == 3 ~ "Asian",
      frace == 4 ~ "Puerto Rican",
      frace == 8 ~ "Other",
      frace == 9 ~ "Unknown"
      )) %>%
  mutate( malform = as.character(malform), malform = case_when(malform == 0 ~ "absent", malform == 1 ~ "present" ))  %>%
  mutate( mrace = as.character(mrace), 
          mrace = case_when(
            mrace == 1 ~ "White", 
            mrace == 2 ~ "Black",
            mrace == 3 ~ "Asian",
            mrace == 4 ~ "Puerto Rican",
            mrace == 8 ~ "Other"
            ))

# Check for missing values?? ~drop_any
```

```{r}
model_1fit = lm(bwt ~ gaweeks, data = Birth_weight_df)
```

```{r}
Residual_predictions = Birth_weight_df %>% 
  modelr::add_residuals(model_1fit) %>% 
  modelr::add_predictions(model_1fit) %>%
  select(resid,pred)

  
Plot = Residual_predictions %>% ggplot(aes(x = resid, y = pred)) + 
  geom_point()
Plot

#X is residuals, y predictions ---> check plot 
```

Compare your model to two others:

-One using length at birth and gestational age as predictors (main effects only)
```{r}
model_2fit = lm(bwt ~ blength + gaweeks, data = Birth_weight_df)
#compare cross validation, graph
```

-One using head circumference, length, sex, and all interactions (including the three-way interaction) between these
```{r}

model_3fit = lm(bwt ~ bhead * blength * babysex, data = Birth_weight_df) 

cv_df = 
  crossv_mc(Birth_weight_df, 100) 

cv_df = 
  cv_df %>% 
  mutate(
   model_3fit  = map(train, ~lm(bwt ~ bhead * blength * babysex, data = Birth_weight_df)), 
   model_2fit = map(train, ~lm(bwt ~ blength + gaweeks, data = Birth_weight_df)),
   model_1fit = map(train, ~lm(bwt ~ gaweeks, data = Birth_weight_df))) %>%
  mutate(
    rmse_3fit = map2_dbl(model_3fit, test, ~rmse(model = .x, data = .y)),
    rmse_2fit = map2_dbl(model_2fit, test, ~rmse(model = .x, data = .y)),
    rmse_1fitl = map2_dbl(model_1fit, test, ~rmse(model = .x, data = .y)))

Compare_model_Plot = cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
Compare_model_Plot

```


##Problem 3

Import Data
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

Use 5000 bootstrap samples and, for each bootstrap sample, produce estimates of these two quantities. Plot the distribution of your estimates, and describe these in words. 

```{r}
boot_sample = function(df) {
  sample_frac(df, replace = TRUE)
}

boot_straps = 
  tibble(
    strap_number = 1:100,
    strap_sample = rerun(100, boot_sample(weather_df))
  )

# Plot 1

beta_results = 
  boot_straps %>%
  mutate(
      models =  map(.x = strap_sample, ~lm(tmax ~ tmin, data = .x)),
      results2 = map(models, broom::tidy)) %>%
  select(strap_number, results2) %>%
  unnest(results2) 

beta_results_plot = beta_results %>%
  ggplot(aes( x = estimate)) + geom_density()
beta_results_plot

#Plot 2

rsquared_results = 
   boot_straps %>%
  mutate(
      models =  map(.x = strap_sample, ~lm(tmax ~ tmin, data = .x)),
      results = map(models, broom::glance)) %>%
  select(strap_number, results) %>%
  unnest(results) 

rsquared_results_plot = rsquared_results %>%
  ggplot(aes( x = r.squared)) + geom_density()
rsquared_results_plot
```

Both plots seem to show an inverse relationship as the density for estimate values for B0 and B1 is a positive parabola with an inflection point at estimate x = 4 and another at approximately x = 7. The r-squared value is a positive parabola value with an inflection point around x = 0.91

# Identify the 2.5% and 97.5% quantiles to provide a 95% confidence interval for r̂ 2 and log(β̂ 0∗β̂ 1). 
```{r}
betas = beta_results %>% select(estimate, strap_number, term)  %>%
  pivot_wider(names_from = term, values_from = estimate)

Conf_Intervals = left_join(betas, rsquared_results, by = "strap_number") %>%
   select(r.squared,`(Intercept)`,tmin, strap_number) %>%
  mutate( beta = log(.[2] * tmin)) 

#95%  for r̂ 2
    ci_lower = quantile(Conf_Intervals$r.squared, 0.025)
    ci_upper = quantile(Conf_Intervals$r.squared, 0.975)
    
#95% for log(β̂ 0∗β̂ 1)

beta_ci_lower = quantile(Conf_Intervals$beta$`(Intercept)`, 0.025)
beta_ci_upper = quantile(Conf_Intervals$beta$`(Intercept)`, 0.975)

```
The quantiles for the r.squared values are `r ci_lower` for the 2.5% quantiles and `r ci_upper` for the 97.5% quantiles. The quantiles for the log of B0 and B1 values are `r beta_ci_lower` for the 2.5% quantile and `r beta_ci_upper` for the 97.5% quantile.

